A distance metric between histograms through the the Kolmogorov-Smirnov test statistic: specification, measures reference and example uses

### 2015-10-31 paper.tex
terminada repassada completa

\FloatBarrier
\section{Music}
This section presents measures of the $c$ statistic drawn
from the pitches of the notes of classical compositions.
The results reflect music history.
Take, for example, the first line, labeled ``Pale''.
The value of $c$ is increased with the exception of Beethoven
who, indeed, used modalism.
In the second line, labeled ``Bach1'',
the values of $c$ are ever increasing,
and previous $c$ (``Pale'' $\times$ ``Bach1'')
is only exceeded when ``Schoe`` is reached,
which reflects the non-tonal discourse of both
Palestrina and Sch\"onberg.

@@

\FloatBarrier
\section{OS status}
\input{tables/osGeneral}
\input{tables/osDistances}

\FloatBarrier
\section{Conclusions}\label{sec:conc}
The $c'$ metric is robust both to determine if
the distributions underlying the samples are the same
and to quantify the difference between probability distributions.
This work presents a set of benchmarks for making use $c'$.
Example analyses of real phenomena reveal patterns
without any of the training or clusterization usually involved in
classification routines.
Also, for making the analysis with other distributions
and data, or modifications on the measure of $c'$,
the rendering of this document is automatized in software.

@@

\appendix
\section{Software and data specifications}\label{ap:soft}
The measure of $c'$ is implemented in a small function within
the gmane Python package~\cite{gmanePack}.
The routines for generating the tables from simulated and empirical
data are grouped in separated files for easing further uses.

>>>>

\FloatBarrier
\section{Music}
This section presents measures of the $c$ statistic drawn
from the pitches of the notes of classical compositions.
The results reflect music history.
For example, measures of $c$ involving Palestrina
increases with the exception of Beethoven
who, indeed, used modalism.
The values of $c$ related to Bach also increases along time,
and the outcome of the comparison against Palestrina 
is only exceeded when Sch\"onberg is reached,
which reflects the non-tonal discourse of both
Palestrina and Sch\"onberg.

@@

\FloatBarrier
\section{OS status}
This last example expose the statistic $c$ for samples drawn from
the operational system of my laptop.
The patterns are less neat than on last examples,
but many conclusions can still be reached.
The memory used by the most consuming processes compose
the samples which present the highest values of $c$.
Lowest values of $c$ are related to RAM usage.
Again, the type of samples are mandatory:
they might all be identified by the values of $c$
found in comparison to other samples,
with the exception of the RAM memory.
\input{tables/osGeneral}
\input{tables/osDistances}

\FloatBarrier
\section{Conclusions}\label{sec:conc}
The $c$ metric is robust both to determine if
the distributions underlying the samples are the same
and to quantify the difference between probability distributions
through the samples.
The benchmarks for $c$, given in Section~\ref{sec:simulations},
are useful as references to make sense e.g. of the example analysis
of Section~\ref{sec:empirical}.
This is specially useful for the analysis of real phenomena
without any of the training or clusterization usually involved in
classification routines.
The rendering of this article, and all tables,
is automated through Python scripts in order to ease modifications
such as the use of other distributions
and data, or modifications on the measure of $c$.

@@

\appendix
\section{Software and data specifications}\label{ap:soft}
The measure of $c$ is implemented in a small function within
the gmane Python package~\cite{gmanePack}.
The routines for generating the tables from simulated and empirical
data are grouped in separated files for easing further use.

### 2015-10-31 tables/osGeneral.tex
terminada repassada completa

\begin{table}[!h]
\begin{center}
\begin{tabular}{| l | c | c |}\hline
label & description & events \\\hline
cpu1 & workload of the most active processor  & 1316.00 \\\hline
cpu2 & workload of the second most active processor  & 529.00 \\\hline
cpu3 & workload of the third most active processor  & 1565.00 \\\hline
mem & RAM use in kB  & 883.00 \\\hline
p1 & workload use of most consuming process  & 1777.00 \\\hline
m1 & RAM use of most consuming process  & 1777.00 \\\hline
p2 & workload use of second most consuming process  & 1777.00 \\\hline
m2 & RAM use of second most consuming process  & 1777.00 \\\hline
p3 & RAM use of third most consuming process  & 1777.00 \\\hline
m3 & workload use of third most consuming process  & 1777.00 \\\hline
\end{tabular}
\caption{General description of the laptop system status data used for the $c'$ values of the next table. Each event is a measure in a snapshot of system status.}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c |}\hline
label & description & events \\\hline
cpu1 & workload of the most active processor  & 888.00 \\\hline
cpu2 & workload of the second most active processor  & 422.00 \\\hline
cpu3 & workload of the third most active processor  & 1046.00 \\\hline
mem & RAM use in kB  & 557.00 \\\hline
p1 & workload use of most consuming process  & 1197.00 \\\hline
m1 & RAM use of most consuming process  & 1197.00 \\\hline
p2 & workload use of second most consuming process  & 1197.00 \\\hline
m2 & RAM use of second most consuming process  & 1197.00 \\\hline
p3 & RAM use of third most consuming process  & 1197.00 \\\hline
m3 & workload use of third most consuming process  & 1197.00 \\\hline
\end{tabular}
\caption{General description of the laptop system status data used for the $c$ values of the next table. Each event is a measure in a snapshot of system status.}
\end{center}
\end{table}
